Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-09-08 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Update rain data pulling for newest version of countyweather

```{r compare_rain_ex_counties, echo = FALSE, fig.width = 10, fig.height = 10, efig.align = "center", fig.cap = "Comparison of rain estimates for example counties."}
plot_county_rain_compare <- function(ex_fips, ex_dir, ex_title, 
                                     get_data = FALSE){
        if(get_data){
                county_timeseries(ex_fips, percent_coverage = 0,
                                  date_min = "1988-01-01",
                                  date_max = "2011-12-31",
                                  var = "PRCP",
                                  out_directory = ex_dir)
        }

@@

        ex_weather <- readRDS(paste0(ex_dir, ex_fips, ".rds"))
        ex_weather <- as.data.frame(ex_weather$daily_weather)

@@

        ex_rain <- county_rain(counties = ex_fips,
                               start_year = 1988, end_year = 2011,
                               rain_limit = 0, dist_limit = 500) %>%
                full_join(ex_weather, by = "storm_id") %>%
                filter(!is.na(prcp) & !is.na(tot_precip))

        ave_n <- round(mean(ex_rain$ave_n, na.rm = TRUE))
        n_storms <- nrow(ex_rain)
        ex_title <- paste0(ex_title, "\n(", n_storms, "; ", ave_n, ")")

>>>>

```{r compare_rain_ex_counties, echo = FALSE, fig.width = 10, fig.height = 10, efig.align = "center", fig.cap = "Comparison of rain estimates for example counties."}
plot_county_rain_compare <- function(ex_fips, ex_dir, ex_title, 
                                     get_data = FALSE){
        if(get_data){
                daily_timeseries(ex_fips, coverage = 0,
                                  date_min = "1988-01-01",
                                  date_max = "2011-12-31",
                                  var = "PRCP",
                                  out_directory = ex_dir)
        }

@@

        ex_weather <- readRDS(paste0(ex_dir, ex_fips, ".rds"))
        ex_weather <- as.data.frame(ex_weather$daily_data)

@@

        ex_rain <- county_rain(counties = ex_fips,
                               start_year = 1988, end_year = 2011,
                               rain_limit = 0, dist_limit = 500) %>%
                full_join(ex_weather, by = "storm_id") %>%
                filter(!is.na(prcp) & !is.na(tot_precip)) %>%
                mutate(prcp = prcp / 10) ## Units for countyweather are now 10ths
                                         ## of millimeters for precipitation

        ave_n <- round(mean(ex_rain$ave_n, na.rm = TRUE))
        n_storms <- nrow(ex_rain)
        ex_title <- paste0(ex_title, "\n(storms: ", n_storms,
                           "; monitors:", ave_n, ")")
